Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-03 thesis/chapters/ch_chapter4.tex
FIxed citation typo. Fixed reference with same first name authors

Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) (references) and begin investigating their chemical properties \citep{Jeon2017,Corlies2018,Escala2018}. Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,Haynes2019} and semi-analytic models \citep{Beniamani2018,KrumholzTing2018}. In \cite{Emerick2018b} we demonstrate that elements released through AGB winds have both wider abundance distributions in the ISM and lower ejection fractions from the galaxy than elements released in supernovae. It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions. In spite of this progress, there is still substantial work to be done in understanding the physical processes that drive both evolution of both the mean and width of stellar abundances in low-mass dwarf galaxies.

>>>>

Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) (references) and begin investigating their chemical properties \citep{Jeon2017,Corlies2018,Escala2018}. Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,HaynesKobayashi2019} and semi-analytic models \citep{Beniamini2018,KrumholzTing2018}. In \cite{Emerick2018b} we demonstrate that elements released through AGB winds have both wider abundance distributions in the ISM and lower ejection fractions from the galaxy than elements released in supernovae. It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions. In spite of this progress, there is still substantial work to be done in understanding the physical processes that drive both evolution of both the mean and width of stellar abundances in low-mass dwarf galaxies.
